SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v16]

### 2015-09-01 paper.tex
added Ken's feedback, changed One Class SVM, added discussion on hyperparameters

\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v15]}

\author{Michael Laskey$^1$, Sam Staszak, Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny, anca\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}

\begin{document}

@@

\begin{abstract}
Online algorithms for robot model-free learning from demonstration (such as DAgger) can learn policies for problems where system
dynamics and cost function are unknown. However, they impose a burden on supervisors to demonstrate labels (control
signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states. SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.  To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.  We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation of consisting of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented as a transformation matrix .  Results suggest that SHIV can learn policies and reduce operator burden significantly  up to 70$\%$.

@@

In \emph{model-free} robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment as shown in Fig. \ref{fig:teaser}, from examples provided by a competent \emph{supervisor}, usually a human. The problem is model-free if  the system dynamics are unspecified, eg. dynamics model may be highly non-linear or noisy. In learning from demonstration, the cost function, which is the negative of the reward function, is usually unknown or significantly delayed. In the grasping for clutter example, shown in Fig. \ref{fig:teaser}(b) the robot is only penalized when an object is knocked off the table, which means a potentially large number of states can be visited before any feedback. To avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls by observing \cite{argall2009survey}.

In the standard supervised setting, a policy is learned offline from a fixed set of examples. When the robot executes this policy, the sequential process can quickly evolve away from the initial set of states.  The learned policy is not helpful in unfamiliar states, leading to robot failures (crashes or dropping objects).  For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states on the side of the road where it has not encountered before, where its policy could  fail \cite{pomerleau1989alvinn}. Theoretically, the number of errors made by the robot in such cases  can scale quadratically with the time horizon of the task \cite{ross2010efficient}.

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/teaser.pdf}
\caption{ 
\todo{update figure}
For a given budget of human supervision, SHIV improves performance (reduced policy cost) in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a surgeon's demonstrations of correcting a needle before suturing in surgery. 
}
\vspace*{-10pt}
\label{fig:teaser}
\end{figure}

\emph{On-line} learning from demonstration approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}. In DAgger, a series of policies are learned.  In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for the  new states, which are then aggregated with the previous examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. Theoretical analysis of DAgger have shown the number of errors to scale linearly for strongly convex loss functions.

One drawback is that such online algorithms increase the burden on the supervisor. Our goal is to reduce supervisor burden without degrading robot performance, \emph{by only requesting demonstrations for risky states. }

Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that have been misclassified, in previous training data.
%\adnote{Ken's version below does not seem to represent what we actually do.}
%the action associated with a state under the current policy yield a resulting state that is inconsistent with the expected next state. [how do we measure 2? - Ken]

@@

We compare SHIV with DAgger in three experiments: 1) a driving simulator, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion. Our analysis suggests that compared to DAgger, SHIV learns a policy that performs significantly better given the same amount of human supervision. Conversely, SHIV significantly reduces supervisory burden (by a factor of $70\%$) while achieving the same performance.

@@

\noindent\textbf{Active Learning from Demonstration}
Online learning from demonstration can be formulated as a \emph{stream-based} active learning problem ~\cite{atlas1990training,cohn1994improving}. In stream based active learning, the decision of whether to query the supervisor (for a control signal or not) is not over the entire state space (like in traditional pool-based active learning), but only on the states encountered during learning.

@@

In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating risk based on \emph{novelty} (is the state an outlier to the training distribution), as in Fig. \ref{fig:support_example}(c). Additionally, we also assign higher risk to  historically \emph{mislabeled} regions, as in Fig. \ref{fig:support_example}(d). We then use a classification method based on the One Class SVM \cite{scholkopf2001estimating} to predict if a state is risky or not risky, which we we define as safe.%Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.

\noindent\textbf{Risk via Novelty Detection.}
One part of our risk definition is the notion that a trained model will be able to generalize within the distribution it is
trained on \cite{tokdar2010importance}. Novelty detection \cite{hodge2004survey} is concerned with recognizing that a sample is outside of this distribution.
One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled. The if the probability of that point is low with respect to the underlying density, it will be marked as novel. However, the amount of data needed to accurately do so scales exponentially in the number of dimensions \cite{nadaraya1964estimating}.

@@

\section{Problem Statement}
The goal of this work is to learn a policy such that it becomes close or identical to a supervisor's policy, such that for states visited after completion of training the action taken by the robot is similar to that of the supervisor.

\noindent\textbf{Assumptions} We assume a system that has a known markovian state space and set of controls. We assume stochastic dynamics of the environment, that are stationary (i.e. the underlying distribution doesn't change over time). We assume access to a robot or simulator, such that we can start in some initial state and apply a series of controls and observe the following states that occur. We assume the initial state must be sampled from some unknown distribution over the state space. Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories initially and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.

\noindent\textbf{Policies and State Densities.}
We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example, of \mlnote{We should discuss if we are going to consider images states or not}
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or
continuous. We assume Markovian dynamics, such that the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
\mathcal{U}$: 
$$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
We assume a probability density over initial states $p(\bx_0)$.
%We denote the probability density over the initial state also by $p:\mathcal{X}\to \mathbb{R}$.

@@

Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
$\pi_{\theta}$ from time $0$ to time $t-1$. This density can be computed by marginalization: $p(\bx_t|\theta) =
\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
the average density on states for \emph{any} timepoint by 
\begin{equation}
p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)
\label{eq:density}
\end{equation}

@@

\noindent\textbf{Objective.} The objective of policy learning is to find a policy that minimizes some known cost function
$C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
be considered \cite{levine2015end}.  
In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
a `supervisor' that we assume uses some $\tilde{\pi}$ to minimize $C(\hat{\tau})$, to an acceptable level. \mlnote{the last statement is intended to mean implementors of this algorithm have agreed that the supervisor may not be optimal, but has a level of performance that is worth automating} We are furthermore given
an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
which are the result of the supervisor applying this policy. This induces a training dataset $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.

@@

Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states. However, instead of querying the supervisor for every new state, SHIV will actively decide whether the state is risky to warrant a query.

@@

SHIV only asks for supervision on states for which $g(\bx)=-1$:

@@

Dagger has been experimentally shown to perform well in both simulation and real world
    experiments\cite{NIPS2014_5421,ross2010reduction,ross2013learning}. Under a `no regret' assumption, Ross et al.\cite{ross2010reduction} furthermore
deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically. For a conservative $\sigma$, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary. However, if $\sigma$ is too high, then SHIV will not collect new data that is needed and revert back to the performance of offline methods. We analyze the dependence on $\sigma$ in Sec. \ref{sec:car}. Our results suggest that SHIV is robust to this parameter selection.

@@

The One Class SVM proposed by \cite{scholkopf2001estimating} determines a hyperplane in feature space $\mathcal{F}$
maximally separating the input data from the origin:
\vspace{-2ex}
\begin{align}\label{eq:primal_sup}
    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag.
\end{align}

Here, the parameter $\nu$ controls the penalty or `slack term' and asymptotically approaches $\gamma$ \cite{vert2006consistency}
in the quantile definition when bandwidths decay at appropriate rates as the number of samples increases. The decision
function, determining point membership in the approximate quantile levelset is given by

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g_{\sigma}(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
\end{align}

Here, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
$g(x) = 1$ if $x$ is strictly in the interior of the quantile super-levelset and $g(x) = -1$ 
if $x$ lies strictly in the quantile sub-levelset. The dual form of the optimization yields a Quadratic Program 
that can be solved efficiently \cite{scholkopf2001estimating}.

For training data in $\mathcal{X}$, we consider the quantile super-levelset for a user-defined threshold $\mu$ as a natural region within which
a trained policy $\pi_{\theta}$ can likely be learned since a sufficient data-density is available.
However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
optimizing Eq. \ref{eq:super_objj} may still incur a large surrogate loss. To account for this, we propose a
modification to the One Class SVM:

\begin{align}
y_i = \left\{
     \begin{array}{lr}
         1 & : l(\pi_{\theta}(\bx_i),\bu_i)\le \varepsilon\\
         -1 & : l(\pi_{\theta}(\bx_i),\bu_i)>\varepsilon
     \end{array}
   \right.
\end{align}
Where, in the case when $l$ denotes discrete $0-1$ loss, we set $\varepsilon = 0$, while in the continuous $L_2$ loss
case, $\varepsilon$ is a user defined threshold specifying allowable surrogate loss.
We use $y_i$ to modify the One Class SVM optimization objective as follows:

\vspace{-2ex}
\begin{align}\label{eq:primal_sup}
    \underset{w\in F, \mathbf{\xi} \in \mathbb{R}^l, \rho \in \mathbb{R}}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
\mbox{s.t} \: y_i \langle w,\Phi(x_i)\rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \label{eq:ineq}.
\end{align}

States that incur loss above the $\varepsilon$ threshold are then enforced to lie on the opposite side of the
hyper-plane separating the origin from the data in the feature space. Practically, this modification corresponds to
`carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
exluded from the super-levelset.

The dual formulation to the modified optimization problem, which is solved in practice, is 
\begin{align}\label{eq:dual_sup}
\underset{\alpha_i\in \mathbb{R}}{\mbox{min}} \sum_i^n \sum_j^n \alpha_i\alpha_j y_i y_jk(\bx_i,\bx_j)\\
\mbox{s.t} \: 0 \leq \alpha \leq \frac{1}{\nu n} \:, \sum_i^n \alpha_i = 1.
\end{align}

Our corresponding decision function $g_{\sigma}:\mathcal{X}\to \mathbb{R}$ is then derived in terms of the support vectors as $$g_{\sigma}(\bx) = \sum_i^n
\alpha_i y_i k(\bx_i,\bx) - \rho$$
To compute the $\rho$ term, we leverage the fact that for an optimal solution the
inequalities in Eq. \ref{eq:ineq} are equal for any $\alpha_j$ such that $0 < \alpha_j < \frac{1}{\nu n}$. Therefore we
can compute $\rho$ as  $\rho = \sum_i^n y_i \alpha_i k(\bx_i,\bx_j)$ \cite{scholkopf2001estimating} {\color{blue} [-- F:
explain this more --]}.

@@

@@

The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
Oriented Gradients (HOG) features using OpenCV. This results in a $27926$ dimensional state space description.
For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.

@@

\begin{table}[t]
\centering
\begin{tabular}{ R{2.5cm}||R{1.65cm}|R{1.65cm} }
 %\hline
 %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
 %\hline 
 \hline
\specialcell{\bf Risk  Sensitivity ($\sigma$)} & \specialcell{\bf Final  Cost} & \specialcell{\bf States  Labeled} \\
 \hline
350 & 13 & 521\\
250 & 6 & 1536 \\
200 & 6 & 1524 \\
150& 6 &  1859 \\
50 & 6 &  3864 \\
1 & 6 & 4122 \\
 %\hline
\end{tabular}
   \caption { \footnotesize  An analysis of the sensitivity of $\sigma$. SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks. As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but worst performance similar to the traditional supervise learning approach. 
   }
		\tablabel{opt-p-comparison}
		\label{tab:sens}

>>>>

\title{SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations [v16]}

\author{Michael Laskey$^1$, Sam Staszak$^3$, Wesley Yu-Shu Hsieh$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^1$, Anca Dragan$^1$, Ken Goldberg$^{1-2}$% <-this % stops a space
\thanks{$^1$ Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey,iamwesleyhsieh, ftpokorny, anca\}@berkeley.edu}}%
\thanks{$^2$ Department of Industrial Engineering and Operations Research; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}
\begin{document}

@@

\begin{abstract}
Online algorithms for robot model-free learning from demonstration (such as DAgger) can learn policies for problems where system
dynamics and cost function are unknown. However, during learning they impose a burden on supervisors to provide labels (control
signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states. SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary high dimensional state distributions.  To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.  We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator with a 27936D visual HOG feature state representation, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D) with a 22D state representation  of joint angles and the pose of each object, and 3) surgical needle insertion with a 16D state represented spatial transform.  Results suggest that SHIV can reduce the number of queries up to 70$\%$.

@@

In model-free robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment as shown in Fig. \ref{fig:teaser}, from examples provided by a competent supervisor, usually a human. The problem is model-free if  the system dynamics are unknown, eg. dynamics model may be highly non-linear or noisy. In learning from demonstration, the cost function, which is the negative of the reward function, is usually unknown or significantly delayed. In the grasping for clutter example, shown in Fig. \ref{fig:teaser}(b) the robot is only penalized when an object is knocked off the table, which means a potentially large number of states can be visited before any feedback. To avoid this a supervisor provides guidance through demonstrations and the robot learns a policy mapping states to controls by observing~\cite{argall2009survey}.

In the supervised setting, a policy is learned offline from a fixed set of examples. When the robot executes this policy, the sequential process can quickly evolve away from the previously explored set of states.  The learned policy might not be helpful in unfamiliar states, leading to unrecoverable failures.  For example, a robot driving may be trained on examples driving safely down the center of a lane, but even slight deviations will put the robot into states near the side of the road where it has not encountered before, where its policy could  fail~\cite{pomerleau1989alvinn}. It has been shown, the number of errors made by the robot in such cases  can scale quadratically with the time horizon of the task~\cite{ross2010efficient}.

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/teaser.pdf}
\caption{ 
\todo{update figure}
SHIV reduces the number of queries to the supervisor in our three test domains: 1) a driving simulator where the goal is to learn a controller on HOG features extracted from synthetic images to keep a car on a polygonal track; 2) push-grasping in clutter in a physics simulator, where the goal is to learn a controller from human demonstrations to grasp the green object while not letting the red square objects fall off the gray boundary representing a table; 3) learning a controller for the Da Vinci Research Kit from a master surgeon's demonstrations of correcting a needle before suturing in surgery. 
}
\vspace*{-10pt}
\label{fig:teaser}
\end{figure}

On-line learning from demonstration approaches such as DAgger iteratively gather more examples from the supervisor~\cite{grollman2007dogged,ross2010efficient,ross2010reduction}. In DAgger, a series of policies are learned.  In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for all  new states, which are then aggregated with the previous examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. It has been shown for DAgger, the number of errors to scale linearly for strongly convex loss functions.

One drawback is that such online algorithms increase the burden on the supervisor. Our goal is to reduce supervisor burden without degrading robot performance, by only requesting demonstrations for risky states.

Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers~\cite{hodge2004survey}; or (2) states are in a region that have been misclassified, in previous training data.
%\adnote{Ken's version below does not seem to represent what we actually do.}
%the action associated with a state under the current policy yield a resulting state that is inconsistent with the expected next state. [how do we measure 2? - Ken]

@@

@@

\noindent\textbf{Active Learning from Demonstration}
Online learning from demonstration can be formulated as a stream-based active learning problem ~\cite{atlas1990training,cohn1994improving}. In stream based active learning, the decision of whether to query the supervisor (for a control signal or not) is not over the entire state space (like in traditional pool-based active learning), but only on the states encountered during learning.

@@

In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating risk based on \emph{novelty} (is the state an outlier to the training distribution), as in Fig. \ref{fig:support_example}(c). Additionally, we also assign higher risk to  historically mislabeled regions, as in Fig. \ref{fig:support_example}(d). We then use a classification method based on the One Class SVM \cite{scholkopf2001estimating} to predict if a state is risky or not risky, which we we define as safe.%Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}.

\noindent\textbf{Risk via Novelty Detection.}
One part of our risk definition is the notion that a trained model will be able to generalize within the distribution it is
trained on \cite{tokdar2010importance}. Novelty detection \cite{hodge2004survey} is concerned with recognizing that a sample is outside of this distribution.
One approach to novelty detection is to directly estimate the underlying probability density function from which the data is sampled. If the probability of that point is low with respect to the underlying density, it will be marked as novel. However, the amount of data needed to accurately do so scales exponentially in the number of dimensions \cite{nadaraya1964estimating}.

@@

\section{Problem Statement}
The goal of this work is to 1)learn a policy, such that for states visited after completion of training the difference in controls taken by the robot is as small as possible to that of the supervisor 2)the supervisor is only requested for a query in states, which the robot is mis-predicting the supervisor's control.

\noindent\textbf{Modeling Choices and Assumptions} We model the system dynamics as markovian and stochastic. The system dynamics are model to be stationary (i.e. given a state and a control the probability of the next state doesn't change over time). We model the initial state as sampled from a distribution over the state space.

We assume a known state space and set of controls. We assume access to a robot or simulator, such that we can start in some initial state and apply a series of controls and observe the following states that occur.  Lastly, we assume access to a supervisor that can provide a series of demonstrated trajectories initially and can be given a state visited by the robot or simulator and provide a control signal of what the supervisor would do.

\noindent\textbf{Policies and State Densities.}
We denote by $\mathcal{X}$ the set consisting of observable states for a robot task, consisting, for example, of \mlnote{We should discuss if we are going to consider images states or not}
high-dimensional vectors corresponding to images from a camera, or robot joint angles and object poses in the environment.
We furthermore consider a set $\mathcal{U}$ of allowable control inputs for the robot, which can be discrete or
continuous. We assume Markovian dynamics, such that the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in
\mathcal{U}$: 
$$p(\bx_{t+1}|\bu_{t},\bx_{t}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{t+1}|\bu_{t}, \bx_t)$$
We assume a probability density over initial states $p(\bx_0)$.
%We denote the probability density over the initial state also by $p:\mathcal{X}\to \mathbb{R}$.

@@

Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
$\pi_{\theta}$ from time $0$ to time $t-1$. This density can be computed by marginalization: $p(\bx_t|\theta) =
\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
the average density on states for any timepoint by 
\begin{equation}
p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)
\label{eq:density}
\end{equation}

@@

\noindent\textbf{Objective.} The objective of policy learning is to find a policy that minimizes some known cost function
$C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
For example, in task of inserting a peg into a hole, a function on distance between the peg's current and desired final state can
be considered \cite{levine2015end}.  
In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
a `supervisor' that we assume uses some $\tilde{\pi}$ to minimize $C(\hat{\tau})$, to an acceptable level. \mlnote{the last statement is intended to mean implementors of this algorithm have agreed that the supervisor may not be optimal, but has a level of performance that is worth automating} We are furthermore given
an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
which are the result of the supervisor applying this policy. This induces a training dataset $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories.

@@

Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1) compute a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states. However, instead of querying the supervisor for every new state, SHIV actively decides whether the state is risky to warrant a query.

@@

SHIV only asks for supervision on states for which $g_{\sigma}(\bx)=-1$:

@@

Dagger has been experimentally shown to perform well in both simulation and real world
    experiments~\cite{NIPS2014_5421,ross2010reduction,ross2013learning}. Under a `no regret' assumption, Ross et al.\cite{ross2010reduction} furthermore
deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically. For a conservative $\sigma$, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary. However, if $\sigma$ is too high, then SHIV will not collect new data that is needed and revert back to the performance of offline methods. We analyze the dependence on $\sigma$ in Sec. \ref{sec:car}. Our results suggest that SHIV is robust to this parameter selection.

@@

The One Class SVM proposed by \cite{scholkopf2001estimating} determines a hyperplane in feature space $\mathcal{F}$
maximally separating the input data from the origin:
\vspace{-2ex}
\begin{align}\label{eq:primal_sup}
    \underset{w\in \mathcal{F}, \mathbf{\xi} \in \mathbb{R}, \rho \in \mathbb{R}}{\mbox{minimize}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag.
\end{align}

Here, the parameter $\nu$ controls the penalty or `slack term' and is equivalent to $\gamma$ \cite{vert2006consistency}
in the quantile definition when bandwidths decay at appropriate rates as the number of samples increases. The decision
function, determining point membership in the approximate quantile levelset is given by

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g_{\sigma}(\bx) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
\end{align}

Here, for $x\in \mathcal{X}$, $g(x)=0$ if $x$ lies on the quantile levelset,
$g(x) = 1$ if $x$ is strictly in the interior of the quantile super-levelset and $g(x) = -1$ 
if $x$ lies strictly in the quantile sub-levelset. The dual form of the optimization yields a Quadratic Program 
that can be solved efficiently \cite{scholkopf2001estimating}. In the dual the decision function is given by

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g(\bx) = \mbox{sgn}(\sum^N_{i=1}\alpha_i k(\bx_i,\bx)-\rho).
\end{align}

where $\alpha_i$ corresponds to the dual variables.    For training data in $\mathcal{X}$, we consider the quantile super-levelset for a user-defined threshold $\mu$ as a natural region within which
a trained policy $\pi_{\theta}$ can likely be learned since a sufficient data-density is available.
However, even when sufficient data is available, the associated control inputs may be inconsistent or noisy and a resulting policy
optimizing Eq. \ref{eq:super_objj} may still incur a large surrogate loss. To account for this, we propose a
modification to the One Class SVM:

\begin{align}
y_i = \left\{
     \begin{array}{lr}
         1 & : l(\pi_{\theta}(\bx_i),\bu_i)\le \varepsilon\\
         -1 & : l(\pi_{\theta}(\bx_i),\bu_i)>\varepsilon
     \end{array}
   \right.
\end{align}

Where, in the case when $l$ denotes discrete $0-1$ loss, we set $\varepsilon = 0$, while in the continuous $L_2$ loss
case, $\varepsilon$ is a user defined threshold specifying allowable surrogate loss.
We use $y_i$ to modify the One Class SVM decision function as follows:

We then divide up our data in two sets those correctly classified:
$$D_{g}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=1\}$$
and those states incorrectly classified: 
$$D_{b}=\{\lbrace \bx_i,\bu_i \rbrace \in \mathcal{D}_{k}, y=-1\}$$
A separate One-Class SVM is then trained on each set of states, ($D_{g}$ and $D_{b}$) and providing measures of the level sets, $g_{\sigma_g}$ and $g_{\sigma_b}$.

We then define the overall decision function as:
$$g_{\sigma}(\bx) = g_{\sigma_g} (\bx)+ g_{\sigma_b}(\bx)$$
points are deemed risky if $g_{\sigma}(\bx) \neq 0$.  Practically, this modification corresponds to
`carving out holes' in the estimated quantile super-levelset such that neighborhoods around states with $y_i=-1$ are
excluded from the super-levelset.

@@

Our modified One Class SVM contains two different $\nu$ parameters, $\nu$ and $\nu_g$. We set $\nu = 1e-3$ and $\nu_g = 1e-1$ for all experiments. The intuition for this is that 'hole-punching' One Class SVM, $g_{\sigma_b}$, should treat all points as inliers, to be conservative. The level set estimation should be robust to outliers in the dataset thus only looks at $90\%$ of points. We tuned $\sigma$ and $\sigma_b$ by doing a grid search over different values on the surrogate loss for a single trial of SHIV for 3 iterations for each example. \mlnote{we start the grid search with a rule of thumb that it should scale with feature size, hence the car example is 200 while the grasping is 5 and the needle is 2, looking for a citation on this though. Scikit learn does the same thing for kenerlized regression}

@@

The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
Oriented Gradients (HOG) features using OpenCV. This results in a $27926$ dimensional state space description.
For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
exponential kernel with a bandwidth of $\sigma_g = 200$ and $\sigma_b = 200$ to account for $95\%$ of the training distribution.

@@

\begin{table}[t]
\centering
\begin{tabular}{ R{2.5cm}||R{1.65cm}|R{1.65cm} }
 %\hline
 %\multicolumn{4}{|c|}{Sensitivity Analysis for Convergence to Best Grasp for Thompson sampling} \\
 %\hline 
 \hline
\specialcell{\bf Risk  Sensitivity ($\sigma$)} & \specialcell{\bf Final  Cost} & \specialcell{\bf States  Labeled} \\
 \hline
 1 & 6 & 4122 \\
 50 & 6 &  3864 \\
 150& 6 &  1859 \\
200 & 6 & 1524 \\
250 & 6 & 1536 \\
350 & 13 & 521\\

 %\hline
\end{tabular}
   \caption { \footnotesize  An analysis of the sensitivity of $\sigma$. SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks. As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to a lot less data being used, but worst performance similar to the traditional supervise learning approach. 
   }
		\tablabel{opt-p-comparison}
		\label{tab:sens}
